Protein Expression

### 2023-11-27 analysis/blots.qmd
analyze blot ratios

@@

@@

@@

@@

@@

@@

@@

>>>>

```{r}
#| label: exp_dual_p_akt
#| fig-width: 4
#| fig-height: 2.5

tar_read(blot_plot_dual_p_akt)
```

@@

```{r}
#| label: exp_dual_p_ampk
#| fig-width: 4
#| fig-height: 2.5

tar_read(blot_plot_dual_p_ampk)
```

@@

```{r}
#| label: exp_dual_p_erk
#| fig-width: 4
#| fig-height: 2.5

tar_read(blot_plot_dual_p_erk)
```

@@

```{r}
#| label: exp_dual_p_smad3
#| fig-width: 4
#| fig-height: 2.5

tar_read(blot_plot_dual_p_smad3)
```

@@

```{r}
#| label: prot_dual_p_akt
#| fig-width: 4
#| fig-height: 2.5

tar_read(blot_plot_dual_p_akt)
```

@@

```{r}
#| label: prot_dual_p_ampk
#| fig-width: 4
#| fig-height: 2.5

tar_read(blot_plot_dual_p_ampk)
```

@@

```{r}
#| label: prot_dual_p_erk
#| fig-width: 4
#| fig-height: 2.5

tar_read(blot_plot_dual_p_erk)
```

@@

```{r}
#| label: prot_dual_p_smad3
#| fig-width: 4
#| fig-height: 2.5

tar_read(blot_plot_dual_p_smad3)
```
